---
title: 'Spatial Analysis: Columbus Crime'
author: "Mary Isangediok"
date: "2022-09-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Spatial Analysis

```{r}
rm(list=ls())
library(spdep)
library(spatialreg)
require(maptools)
require(rgdal)
```

## Load data

Set work directory and plot data

```{r}
setwd("C:\\Users\\maryp\\Downloads\\Spatial_Analysis_Columbus_Crime")
unzip("columbus.zip")
CC = readOGR(dsn = ".", layer = "columbus")
## check data
slotNames(CC)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Plot spatial data

```{r}
df = CC@data
## SSPLOT
plot(CC)
spplot(CC, "CRIME", pretty = TRUE)
```

## Plot Columbus crime data

```{r}
require(RColorBrewer)
range(CC$CRIME)
rng = seq(0, 70, 10)
cls = brewer.pal(7, "Greens")
spplot(CC, "CRIME", col.regions = cls, at = rng, sub = "Crime Data in Ohio")
```

## Plot neighbor coordinates for data

```{r}
data(columbus)  
help(columbus)
mydata <- columbus
attach(mydata)
Y <- cbind(CRIME)
X <- cbind(INC, HOVAL)
xy <- cbind(mydata$X, mydata$Y)
neighbors <- col.gal.nb
coords <- coords
# Neighbors summary
summary(neighbors)
plot(neighbors, coords)
```

## Descriptive statistics

```{r}
summary(Y)
summary(X)
```

## OLS Regression

```{r}
olsreg <- lm(Y ~ X)
summary(olsreg)
```

## Spatial analysis based on contiguity

```{r}
# Spatial weight matrix based on contiguity
listw <- nb2listw(neighbors)
summary(listw)
```

```{r}
# Moran's I test
moran.test(CRIME, listw)
moran.plot(CRIME, listw)
```

```{r}
# Lagrange multiplier test for spatial lag and spatial error dependencies
lm.LMtests(olsreg, listw, test=c("LMlag", "LMerr"))
```

```{r}
# Spatial lag model
spatial.lag <- lagsarlm(CRIME ~ INC + HOVAL, data = mydata, listw)
summary(spatial.lag)
```

```{r}
# Spatial error model
spatial.error <- errorsarlm(CRIME ~ INC + HOVAL, data = mydata, listw)
summary(spatial.error)
```
## Spatial analysis based on distance weight matrix

```{r}
# Spatial weight matrix based on distance (with lower and upper bounds for distance, d1 and d2)
nb <- dnearneigh(xy, d1=0, d2=10)
listw <- nb2listw(nb, style="W")
summary(listw)
```

```{r}
# Moran's I test
moran.test(CRIME, listw)
moran.plot(CRIME, listw)
```

```{r}
# Lagrange multiplier test for spatial lag and spatial error dependencies
lm.LMtests(olsreg, listw, test=c("LMlag", "LMerr"))
```




```{r}
# Spatial lag model
spatial.lag1 <- lagsarlm(CRIME ~ INC + HOVAL, data = mydata, listw)
summary(spatial.lag1)
```

```{r}
# Spatial error model
spatial.error1 <- errorsarlm(CRIME ~ INC + HOVAL, data = mydata, listw)
summary(spatial.error1)
```
